Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
spell checking

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accomodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suites exist for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests constantly fail on the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the aproach is that
it can be fully automated. As the same engine is used, the outcomes of
the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). This paper evaluates the potential
benefits of diversity techniques, including DT. It provides data to
support or not the decision for automation of these techniques.

@@

  \item We made our testing infrastructure, results, and experimental
    scripts available to the public. (upon request for anonimity.)

@@

Column ``pass-in-par.'' shows the number of test cases that pass in
their parent engine. We discarded tests that fail in their parent
engine as we could not reliably indicate the reason for the failure,
so we assumed the test could be broken. We removed 63 test cases that
fail for that reason--6 tests from \jsc{} and 57 tests from
\smonkey. Column ``compile-in-all'' shows the number of test cases
whose executions do not throw errors because of an undefined variable
or property. We capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantion, \ie{}, the
difference between sets ``compile-in-all'' and Test262. We did not
consider tests from the conformance suite as they are more likely to
indicate missing features as opposed to bugs. In addition, engine
developers have access to these test and are encouraged to run
them. Column ``no-fail-in-all'' shows the tests for which all engines
pass. This test set is used in the evaluation of differential
testing. Note that it is a proper subset of the ``compile-in-all''
test set. The tests from this group are used as fuzzing seeds. The
guarantee that they pass in all engines assures that, if discrepancies
occur, they are related to the changes in the input as opposed to the
original cause of failure.

@@

We classified warnings in two types, reflecting their likelihood of
manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
with the cases where the test code executed to completion without
violating any internal checks, but it violated assertions declared in
the test itself or its harness. The rationale is that the input is
more likely to be valid as it it did not raise exceptions during the
execution of the application code, but, it manifested discrepancy
through the violation of an assertion declared in the test. In
contrast, warnings of type ``\lo{}'' are more likely to be asssociated
with invalid inputs. They reflect the cases where the anomaly is
observed during the execution of functions, which are part of the
application. We found that different engines often check
pre-conditions of those functions differently. It can happen, for
example, that one engine enforces a weaker pre-condition on a function
input compared to another engine and that is acceptable.\Comment{ For
  instance, it is acceptable to pass values greater than \Fix{x} to
  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
cases, the infrastructure would observe a discrepancy that is more
likely to be associated with an invalid input produced by the fuzzer,
\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
bug in the engine code. However, as expected, our heuristic is not
precise---``\lo'' warnings can reveal
bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
this example, the test instantiates an \CodeIn{ArrayBuffer} object and
stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception. This
is a case of undocumented precondition, which is handled as a bug. It
was fixed by \chakra\ developers and is no longer present in the most
recent release of \chakra. Despite that case, most bugs we found
emerged from ``\hi{}'' warnings.

@@

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
%% \Mar{igor,
%%   nao consigo entender o porque deste caso nao dar aqueles erros
%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
%% }
%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
%% }
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
  por exemplo cobre uma especificacao antiga onde o
  teste esperava uma propriedade true, mas na documentacao 
  cita que a propriedade tem que ser false.}\Mar{nao
  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
  seja mais especifico, por favor!}
  \Igor{nao, o teste eh valido (nao quebra por ReferenceError/TypeError) e
  nao entra no undefined behaviour pq nao afeta a especificacao. Isso eh um caso,
  outros casos estao ligados a nao-compreensao do testcase }  \textbf{Unknown.} This category
includes the cases we were unable to confidently diagnose the failure
but we suspected it was a false alarm.

@@

\begin{table}[t!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Unknown & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' and ``Non-Standard Element'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.
Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Url'' shows the URL (de-anonymized upon request) for the bug
report entry in the corresponding bug-tracking system, column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\Fix{ten} of the bugs we reported were confirmed, \Fix{two} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was cosidered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. In \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

This section discusses a selection of bugs reports. The selection
criteria we used was: (i) to cover each of the engines we were able to
find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
successful technique--test transplantation and differential testing
(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
rejected bug report, and (iv) the test is short.

@@

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
{var a =
  {valueOf:~function(){ return "\x00"}}
  assert(+a === 0)}
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
\end{figure}

The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in
ascii). The unary plus expression ``\CodeIn{+a}", used in the
assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)~\cite{unary-plus}. This test fails in all engines but
\chakra{}. For all three engines the string cannot be parsed as an
hexadecimal. As such, they produce a NaN as result and the test fails
as expected. \chakra{}, in contrast, incorrectly converts the string
to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

@@

This code snippet was obtained by fuzzing a Test262 test with
\quickfuzz. In its original version, a string (omitted for space),
passed as argument to the \CodeIn{eval} function, encoded the actual
test. The fuzzer replaced the string argument with a function whose
body is a \CodeIn{break} statement outside a valid block
statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
how eval should be handle code containing a function declaration.
According to specification~\cite{break-statement}, the break statement
should throw an early error--in this case a SyntaxError--if the break
statement is not nested in an iterational or a switch statement. In
this case, all engines behave as expected but \veight{} pass without
failures.

@@

As it is the case for most empirical evaluations, there are both
external and construct threats to validity associated to the results
we presented. In terms of external validity, our results might not
generalize to other test inputs and engines. To mitigate this threat,
we carefully selected inputs from various sources and cleaned them
according to a well-defined criteria. Considering the \js\ engines, we
used engines associated with the most popular browsers in the
market. In terms of construct validity, there might be errors in the
implementation of our infrastructure. To mitigate this threat, we
extensively inspected the results of our evaluation manually and, when
we found the need for implementing a different component we kept the
old one for cross-checking. For example, we used
eshost-cli~\cite{eshost-cli} to validate our fork-join implementation
of the ``Checker'' component from Figure~\ref{fig:workflow} that, for
efficiency, is tighly integrated to our infrastructure.

@@

\begin{itemize}
  \item The diversity-aware techniques we used are great
    at finding bugs in \js\ engines;
  \item The cost of inpecting failures/warnings is high. Although the
    inspection activity was not uninterrupted, it is safe to say that
    each warning required a substantial amount of time to analyze for
    potential false alarms;
  \item We have found more bugs with test transplantation than we have
    with cross-engine differential testing. In addition, test
    transplantation demanded less effort per bug;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine we used, with Google's \veight\ after it;
  \item Reporting real bugs is a great way to train (and encourage)
    students in software testing.
\end{itemize}

@@

\subsection{Testing \js{} Engines}
\label{sec:testing-js-engines}
The closest work to ours was done by Patra and
Pradel~\cite{patra2016learning}. Their work proposes a
language-agnostic fuzzer to findcross-browser HTML+JS
discrepancies. Their fuzzer can be used to find bugs in JS engines and
WebAssembly engines. The sensible parts of the infrastructure they
built are the checks of input validity (as to reduce waste/cost) and
output correctness (as to reduce false positives). Patra and Pradel
work is complementary to ours--in principle, we could use their fuzzer
in our evaluation. The main difference of our work to theirs is in
goal--we aim at assessing reliability of \js\ engines and find bugs on
them using simple approaches whereas they aim at proposing a new
technique.

@@

%%  LocalWords:  bytecodes JScript Ecma ome IoT Kangax DT JS fuzzer
%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU
%%  LocalWords:  GoogleChromeLab's cccr js runtime Fuzzers Radamsa de
%%  LocalWords:  QuickFuzz fuzzers Grammarinator LangFuzz Megadeth
%%  LocalWords:  AFL libFuzzer toolchain sanitizers arrowed eshost
%%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC
%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii
%%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
%%  LocalWords:  SSL TLS ICSE

>>>>

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accommodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suites exist for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests constantly fail on the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

@@

\emph{Related Ideas.}  It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.} against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation). A positive aspect of the approach is that
it can be fully automated. As the same engine is used, the outcomes of
the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). This paper evaluates the potential
benefits of diversity techniques, including DT. It provides data to
support or not the decision for automation of these techniques.

@@

  \item We made our testing infrastructure, results, and experimental
    scripts available to the public. (upon request for anonymity.)

@@

Column ``pass-in-par.'' shows the number of test cases that pass in
their parent engine. We discarded tests that fail in their parent
engine as we could not reliably indicate the reason for the failure,
so we assumed the test could be broken. We removed 63 test cases that
fail for that reason--6 tests from \jsc{} and 57 tests from
\smonkey. Column ``compile-in-all'' shows the number of test cases
whose executions do not throw errors because of an undefined variable
or property. We capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantation, \ie{}, the
difference between sets ``compile-in-all'' and Test262. We did not
consider tests from the conformance suite as they are more likely to
indicate missing features as opposed to bugs. In addition, engine
developers have access to these test and are encouraged to run
them. Column ``no-fail-in-all'' shows the tests for which all engines
pass. This test set is used in the evaluation of differential
testing. Note that it is a proper subset of the ``compile-in-all''
test set. The tests from this group are used as fuzzing seeds. The
guarantee that they pass in all engines assures that, if discrepancies
occur, they are related to the changes in the input as opposed to the
original cause of failure.

@@

We classified warnings in two types, reflecting their likelihood of
manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
with the cases where the test code executed to completion without
violating any internal checks, but it violated assertions declared in
the test itself or its harness. The rationale is that the input is
more likely to be valid as it it did not raise exceptions during the
execution of the application code, but, it manifested discrepancy
through the violation of an assertion declared in the test. In
contrast, warnings of type ``\lo{}'' are more likely to be associated
with invalid inputs. They reflect the cases where the anomaly is
observed during the execution of functions, which are part of the
application. We found that different engines often check
pre-conditions of those functions differently. It can happen, for
example, that one engine enforces a weaker pre-condition on a function
input compared to another engine and that is acceptable.\Comment{ For
  instance, it is acceptable to pass values greater than \Fix{x} to
  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
cases, the infrastructure would observe a discrepancy that is more
likely to be associated with an invalid input produced by the fuzzer,
\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
bug in the engine code. However, as expected, our heuristic is not
precise---``\lo'' warnings can reveal
bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
this example, the test instantiates an \CodeIn{ArrayBuffer} object and
stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception. This
is a case of undocumented precondition, which is handled as a bug. It
was fixed by \chakra\ developers and is no longer present in the most
recent release of \chakra. Despite that case, most bugs we found
emerged from ``\hi{}'' warnings.

@@

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omitted standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead.  \textbf{Other.} This category includes
other sources. For example, it includes the cases where the test was
valid for some previous version of the spec but is no longer valid for
the current spec.

@@

\begin{table}[t!]
  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Other & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' was the most predominant source. Considering true
positives, we found a reasonable number of duplicate reports, but not
enough high to justify attempting to automate the detection of
duplicates.  Table~\ref{tab:test-transplantation-bugs} lists all bugs
we found with test transplantation. The first column shows the
identifier we assigned to the bug\Comment{, column ``Date'' shows the
  date the bug was reported in the format ``m/dd'',}, column
``Engine'' shows the affected engine, column ``Status'' shows the
status of the bug report at the time of the writing. The status string
appears in bold face for status ``Confirmed'' or higher, \ie{},
``Assigned'' and ``Fixed''.  Column ``Url'' shows the URL
(de-anonymized upon request) for the bug report entry in the
corresponding bug-tracking system, column ``Severity'' shows the
severity level for confirmed bugs, and, finally, column ``Suite''
shows the name of the engine that originated the test.

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\Fix{ten} of the bugs we reported were confirmed, \Fix{two} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. In \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

This section discusses a selection of bugs reports. The selection
criteria we used was: (i) to cover each engine that we found
bugs--\chakra, \jsc, and \veight, (ii) to cover a different
technique--test transplantation and differential testing (with
\radamsa\ and with \quickfuzz), (iii) to cover a case of rejected bug
report, and (iv) to use short test inputs (for space).

@@

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
{var a =
  {valueOf: function(){ return "\x00"}}
  assert(+a === 0)
}
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
\end{figure}

The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
ascii}. The unary plus expression ``\CodeIn{+a}", used in the
assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)~\cite{unary-plus}. This test fails in all engines but
\chakra{}. For all three engines the string cannot be parsed as an
hexadecimal. As such, they produce a NaN as result and the test fails
as expected. \chakra{}, in contrast, incorrectly converts the string
to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

@@

This code snippet was obtained by fuzzing a Test262 test with
\quickfuzz. In its original version, a string (omitted for space),
passed as argument to the \CodeIn{eval} function, encoded the actual
test. The fuzzer replaced the string argument with a function whose
body is a \CodeIn{break} statement outside a valid block
statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
how eval should be handle code containing a function declaration.
According to specification~\cite{break-statement}, the break statement
should throw an early error--in this case a SyntaxError--if the break
statement is not nested in an iterable or a switch statement. In
this case, all engines behave as expected but \veight{} pass without
failures.

@@

As it is the case for most empirical evaluations, there are both
external and construct threats to validity associated to the results
we presented. In terms of external validity, our results might not
generalize to other test inputs and engines. To mitigate this threat,
we carefully selected inputs from various sources and cleaned them
according to a well-defined criteria. Considering the \js\ engines, we
used engines associated with the most popular browsers in the
market. In terms of construct validity, there might be errors in the
implementation of our infrastructure. To mitigate this threat, we
extensively inspected the results of our evaluation manually and, when
we found the need for implementing a different component we kept the
old one for cross-checking. For example, we used
eshost-cli~\cite{eshost-cli} to validate our fork-join implementation
of the ``Checker'' component from Figure~\ref{fig:workflow} that, for
efficiency, is tightly integrated to our infrastructure.

@@

\begin{itemize}
  \item The diversity-aware techniques we used are great
    at finding bugs in \js\ engines;
  \item The cost of inspecting failures/warnings is high. Although the
    inspection activity was not uninterrupted, it is safe to say that
    each warning required a substantial amount of time to analyze for
    potential false alarms;
  \item We have found more bugs with test transplantation than we have
    with cross-engine differential testing. In addition, test
    transplantation demanded less effort per bug;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine we used, with Google's \veight\ after it;
  \item Reporting real bugs is a great way to train (and encourage)
    students in software testing.
\end{itemize}

@@

\subsection{Testing \js{} Engines}
\label{sec:testing-js-engines}
The closest work to ours was done by Patra and
Pradel~\cite{patra2016learning}. Their work proposes a
language-agnostic fuzzer to findcross-browser HTML+JS
discrepancies. Their fuzzer can be used to find bugs in JS engines and
Web Assembly engines. The sensible parts of the infrastructure they
built are the checks of input validity (as to reduce waste/cost) and
output correctness (as to reduce false positives). Patra and Pradel
work is complementary to ours--in principle, we could use their fuzzer
in our evaluation. The main difference of our work to theirs is in
goal--we aim at assessing reliability of \js\ engines and find bugs on
them using simple approaches whereas they aim at proposing a new
technique.

@@

%%  LocalWords:  bytecodes JScript Ecma ome IoT Kangax DT JS fuzzer
%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU
%%  LocalWords:  GoogleChromeLab's cccr js runtime Fuzzers Radamsa de
%%  LocalWords:  QuickFuzz fuzzers Grammarinator LangFuzz Megadeth
%%  LocalWords:  AFL libFuzzer toolchain sanitizers arrowed eshost
%%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC crr
%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii crrrr
%%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber
%%  LocalWords:  drainMicrotasks subtrees ArrayBuffer RangeError eval
%%  LocalWords:  ToIndex Clusterization DataView setInt getInt boxpos
%%  LocalWords:  JavaScriptCore SpiderMonkey byteOffset anonymized
%%  LocalWords:  xleftmargin framexleftmargin basicstyle numberstyle
%%  LocalWords:  escapeinside morekeywords
